---
title: "Assignment 1"
subtitle: ''
author: "Pablo E. Gutiérrez-Fonseca"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---

### Instructions / Instrucciones generales

- This assignment consists of 10 questions, each worth **10 points**.  
(Esta tarea consta de 10 preguntas, cada una vale **10 puntos**.)

- Complete the assignment using an **R Markdown (.Rmd) document**. Include the **date and time** when you started or completed the assignment in the **YAML header**.
(Completa la tarea utilizando un documento **R Markdown (.Rmd)**. Incluye la **fecha y hora** en que comenzaste o terminaste la tarea en el encabezado YAML.)

- Write your answers in R code chunks whenever applicable.  
(Escribe tus respuestas en chunks de R cuando sea aplicable.)

- Make sure your code runs without errors. Include comments if necessary.  
(Asegúrate de que tu código se ejecute sin errores. Incluye comentarios si es necesario.)

- For questions about chunk options, experiment with the options and write down your observations.  
(Para preguntas sobre opciones de chunks, experimenta con ellas y escribe tus observaciones.)

- Submit the assignment on your personal webpages using the **HTML file** exported/knit from the `.Rmd`.  
Do not copy output screenshots unless requested.  
(Entrega la tarea en tus páginas personales usando el **archivo HTML** generado/kniteado desde el `.Rmd`.  
No copies capturas de pantalla del resultado a menos que se indique.)

- You have until tomorrow, Friday, September 18, at 11:59 PM to submit the assignment. (Tienen hasta mañana, viernes 18 de septiembre, a las 11:59 p. m. para enviar la tarea.)


<br><br><br>

#### **Assigning values**
**Q1.** Create an object called height with the value 175. Print it. (Crea un objeto llamado height con el valor 175. Muéstralo en pantalla.)

<br><br>

#### **Simple math**
**Q2.** Calculate the result of 25 * 4 - 10. (Calcula el resultado de 25 * 4 - 10.)

<br><br>

####  **Using functions**
**Q3.** Use the function sqrt() to calculate the square root of 81. (Usa la función sqrt() para calcular la raíz cuadrada de 81.)

<br><br>

#### **Character objects**
**Q4.** Assign the phrase "R is fun!" to an object called message. Print it. (Asigna la frase "R is fun!" a un objeto llamado message. Muéstralo.)

<br><br>

#### **Object manipulation**
**Q5.** Create two objects a <- 10 and b <- 5. Calculate their sum and store it in c.
(Crea dos objetos a <- 10 y b <- 5. Calcula su suma y guárdala en c.)

<br><br>

#### **Logical comparison**
**Q6.** Test whether 15 is greater than 20.  (Verifica si 15 es mayor que 20.)  

<br><br>

#### **Checking classes**
**Q7.** Check the class of the object `"Hello World"`.  (Verifica la clase del objeto `"Hello World"`.)  

<br><br>

#### **Code chunk options**
**Q8.** Run the following code chunk:  
- Observe the warnings that appear. (Observa las advertencias que aparecen.)  
- Modify the chunk options **to suppress warnings** without changing the code itself. (Modifica las opciones del chunk para **apagar la advertencia** sin cambiar el código.)

```{r}
log(-1)
```

<br><br>

#### **Code chunk options**
**Q9.** Run the following code chunk:
- Observe the messages that appear. (Observa los mensajes que aparecen.)

- Modify the chunk options to suppress messages without changing the code itself.
(Modifica las opciones del chunk para apagar mensajes sin cambiar el código.)
```{r}
# Load a package (may produce messages)
library(dplyr)
```

<br><br>

#### **Creating and analyzing a vector**
Q10. Create a numeric vector called grades containing the values 80, 90, 75, 95, and 85. Then, use the mean() function to calculate the average grade and store the result in an object called average. Print the result.`mean()`.) 
(Crea un vector numérico llamado grades que contenga los valores 80, 90, 75, 95 y 85. Luego, utiliza la función mean() para calcular el promedio y guarda el resultado en un objeto llamado average. Muestra el resultado en pantalla.)

<br><br><br><br><br><br><br><br>



