---
title: "Study Guide: Base R – Basic Plots"
subtitle: ''
author: "Pablo E. Gutiérrez-Fonseca"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---

<br><br>

### **Recordatorio / Warning**
- This study guide does not replace class instruction. It is intended to summarize the most important concepts only. Everything presented in class slides may be included in assessments.
- Esta guía de estudio no sustituye lo visto en clase. Solo pretende resumir los conceptos más importantes. Todo lo que se encuentra en las presentaciones de clase puede ser evaluado.

<br><br>

#### 1. plot(): Basic plotting function
Creates scatterplots, line plots, or combined plots.
```{r eval=FALSE}
plot(x, y)          # scatterplot
plot(x, y, type="l") # line plot
plot(x, y, type="b") # points + lines
```
<br><br>

#### 2. Common graphical parameters
Modify labels, color, size, and axes.
```{r eval=FALSE}
plot(x, y,
     main = "Title",
     xlab = "X axis",
     ylab = "Y axis",
     col = "blue",
     pch = 19,       # point style
     cex = 1.2)      # point size
```
<br><br>

#### 3. hist(): Histograms
Shows distribution of a numeric variable.
```{r eval=FALSE}
hist(x)
hist(x, breaks = 20, col = "gray")
```
<br><br>

#### 4. boxplot(): Distribution and group comparison
```{r eval=FALSE}
boxplot(x)
boxplot(values ~ group)
```
<br><br>

#### 5. barplot(): Simple bar charts
```{r eval=FALSE}
barplot(counts)
```
<br><br>

#### 6. Add elements to a plot
- Useful for annotations or regression lines.
```{r eval=FALSE}
boxplot(x)
boxplot(values ~ group)
```
<br><br>


#### 7. Add elements to a plot
- Useful for annotations or regression lines.
```{r eval=FALSE}
abline(h = 5)              # horizontal line
abline(v = 10)             # vertical line
abline(lm(y ~ x))          # regression line

points(x2, y2, col="red", pch=19)
text(3, 10, "Label here")
```
<br><br>


#### 8. Saving plots
```{r eval=FALSE}
png("base_plot.png", width = 800, height = 600)
plot(x, y)
dev.off()
```
<br><br>

