---
title: "Exam Practice"
subtitle: ''
author: "Pablo E. Gutiérrez-Fonseca"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---

### Load libraries

```{r message=F}
library(readxl)
library(dplyr)
```

### Practice data manupulation using Base R

The data in **cereal.csv** includes nutrition information collected from breakfast cereals. The data, which were provided by (Lock:2020?), were obtained from <http://nutritionresource.com/>.

-   The attributes included in the data are:
    -   name: Brand name of cereal
    -   company: Manufacturer (G=General Mills, K=Kellog’s or Q=Quaker)
    -   serving: Serving size (in cups)
    -   calories: Calories (per cup)
    -   fat: Fat (grams per cup)
    -   sodium: Sodium (mg per cup)
    -   carbs: Carbohydrates (grams per cup)
    -   fiber: Dietary Fiber (grams per cup)
    -   sugars: Sugars (grams per cup)
    -   protein: Protein (grams per cup)

```{r}
cereal <- read_excel("cereal.xlsx")
head(cereal)
```

### Five question (**1 pt each**):

1.  Extract rows 1 to 10 from the cereal data frame.
2.  Create a new data frame called Kelloggs that only contains rows where company == "K".
3.  From the cereal data, extract the names of all cereals that have more than 10 grams of sugar.
4.  Find the mean calories of all cereals in the dataset.
5.  Count how many cereals have fiber greater than or equal to 2 grams.

```{r, include=FALSE}
# 1. Extract rows 1 to 10
cereal[1:10, ]

# 2. Create new data frame with only Kelloggs cereals
Kelloggs <- cereal[cereal$company == "K", ]
Kelloggs

# 3. Names of cereals with more than 10 grams of sugar
cereal$name[cereal$sugars > 10]

# 4. Mean calories of all cereals
mean(cereal$calories)

# 5. Count cereals with fiber >= 2 grams
length(cereal$fiber[cereal$fiber >= 2])
# (alternative: sum(cereal$fiber >= 2))
```

<br><br><br>

### Practice data manupulation using **dplyr** and **ktable**

The data in EquationCitations.csv includes information on the number of equations and citations for evolutionary biology publications. The data were obtained from Fawcett and Higginson (2012) and the online supplement (<https://www.pnas.org/doi/suppl/10.1073/pnas.1205259109/suppl_file/sd01.xlsx> ).

-   The attributes included in the data are:
-   journal: Journal in which the paper was published (The American Naturalist, Evolution, Proceedings of the Royal Society of London B: Biological Sciences)
-   authors: Names of authors
-   volume: Volume in which the paper was published
-   startpage: Starting page of publication
-   pages: Number of pages
-   equations: Number of equations in total
-   mainequations: Number of equations in main text
-   appequations: Number of equations in appendix
-   cites: Number of citations in total
-   selfcites: Number of citations by the authors themselves
-   othercites: Number of citations by other authors
-   theocites: Number of citations by theoretical papers
-   nontheocites: Number of citations by nontheoretical papers

**Details:** Fawcett and Higginson (2012) investigate how the number of equations in evolutionary biology papers affects citation counts. They found that papers with many mathematical equations receive fewer citations, especially from nontheoretical papers.

**Source:** Online supplements to Fawcett and Higginson (2012) <https://www.pnas.org/doi/suppl/10.1073/pnas.1205259109/suppl_file/sd01.xlsx>

**References:** Fawcett, T.W. and Higginson, A.D. (2012). Heavy Use of Equations Impedes Communication among Biologists. PNAS – Proceedings of the National Academy of Sciences of the United States of America, 109, 11735–11739. <doi:10.1073/pnas.1205259109>

```{r}
articles <- read.csv("EquationCitations.csv")
head(articles)
```

### Five question (**2 pts each**):

1.  Summarize by journal. Calculate the average number of equations per article in each journal. Display the results in a nicely formatted table. Hint: `group_by()` and `summarise()`

2.  **Find the top 5 articles** with the **highest number of total cites**. Show the authors, journal, and cites. Hint: `arrange(desc())`, `slice_head()`, and `select()`

3.  Create a new variable eq_ratio = mainequations / (mainequations + appequations). Then, compute the **mean** eq_ratio **per journal** and display in a table. Hint: `mutate()`, `group_by()`, and `summarise()`

4.  Theoretical vs. non-theoretical citations. For each **journal**, calculate the **average proportion of theoretical citations**. Hint: `mutate()`, `group_by()`, `summarise()`

5.  **Filter and summarize short articles.** Filter articles with **fewer than 10 pages**. For these, calculate the **average number of equations** and the **average** number of citations. Hint: `filter()` and `summarise()`

```{r, include= FALSE}
library(dplyr)
library(knitr)

# 1. Summarize by journal: average number of equations
articles %>%
  group_by(journal) %>%
  summarise(avg_equations = mean(equations, na.rm = TRUE)) %>%
  kable(caption = "Average number of equations per article by journal")

# 2. Top 5 articles with highest total cites
articles %>%
  arrange(desc(cites)) %>%
  slice_head(n = 5) %>%
  select(authors, journal, cites) %>%
  kable(caption = "Top 5 articles with highest total citations")

# 3. Create eq_ratio and compute mean per journal
articles %>%
  mutate(eq_ratio = mainequations / (mainequations + appequations)) %>%
  group_by(journal) %>%
  summarise(mean_eq_ratio = mean(eq_ratio, na.rm = TRUE)) %>%
  kable(caption = "Mean eq_ratio per journal")

# 4. Proportion of theoretical citations per journal (simpler version)
articles %>%
  mutate(theo_ratio = theocites / cites) %>%
  group_by(journal) %>%
  summarise(avg_theo = mean(theo_ratio, na.rm = TRUE))

# 5. Filter short articles (<10 pages) and summarize
articles %>%
  filter(pages < 10) %>%
  summarise(
    avg_equations = mean(equations, na.rm = TRUE), 
    avg_cites = mean(cites, na.rm = TRUE)
  ) %>%
  kable(caption = "Average equations and citations for short articles (<10 pages)")

```

<br><br><br>
