---
title: "Exam Practice"
subtitle: ''
author: "Pablo E. Gutiérrez-Fonseca"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---

# Load libraries

```{r}
library(readxl)
```

The data in **cereal.csv** includes nutrition information collected from breakfast cereals. The data, which were provided by (Lock:2020?), were obtained from <http://nutritionresource.com/>.

-   The attributes included in the data are:
    -   name: Brand name of cereal
    -   company: Manufacturer (G=General Mills, K=Kellog’s or Q=Quaker)
    -   serving: Serving size (in cups)
    -   calories: Calories (per cup)
    -   fat: Fat (grams per cup)
    -   sodium: Sodium (mg per cup)
    -   carbs: Carbohydrates (grams per cup)
    -   fiber: Dietary Fiber (grams per cup)
    -   sugars: Sugars (grams per cup)
    -   protein: Protein (grams per cup)

```{r}
cereal <- read_excel("cereal.xlsx")
head(cereal)
```

# Using Base R:

-   Extract rows 1 to 10 from the cereal data frame.
-   Make a new data frame called Kelloggs which only contains rows that belongs to manufacturer, Kellogs (when mfr takes the value “K”).
