---
title: "Exam Practice"
subtitle: ''
author: "Pablo E. Gutiérrez-Fonseca"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---

### Load libraries

```{r message=F}
library(readxl)
library(dplyr)
```

### Practice data manupulation using Base R

The data in **cereal.csv** includes nutrition information collected from breakfast cereals. The data, which were provided by (Lock:2020?), were obtained from <http://nutritionresource.com/>.

-   The attributes included in the data are:
    -   name: Brand name of cereal
    -   company: Manufacturer (G=General Mills, K=Kellog’s or Q=Quaker)
    -   serving: Serving size (in cups)
    -   calories: Calories (per cup)
    -   fat: Fat (grams per cup)
    -   sodium: Sodium (mg per cup)
    -   carbs: Carbohydrates (grams per cup)
    -   fiber: Dietary Fiber (grams per cup)
    -   sugars: Sugars (grams per cup)
    -   protein: Protein (grams per cup)

```{r}
cereal <- read_excel("cereal.xlsx")
head(cereal)
```
<br> 

#### Five question ():

1.  Extract rows 1 to 10 from the cereal data frame. (*Extraiga las filas 1 a 10 del marco de datos cereal.*)
2.  Create a new data frame called Kelloggs that only contains rows where company == "K". (*Cree un nuevo marco de datos llamado Kelloggs que solo contenga las filas donde company == "K".*)
3.  From the cereal data, extract the names of all cereals that have more than 10 grams of sugar. (*Del conjunto de datos cereal, extraiga los nombres de todos los cereales que tienen más de 10 gramos de azúcar.*)
4.  Find the mean calories of all cereals in the dataset. (*Encuentre las calorías promedio de todos los cereales en el conjunto de datos.*)
5.  Count how many cereals have fiber greater than or equal to 2 grams (*Cuente cuántos cereales tienen fibra mayor o igual a 2 gramos.*).

```{r, include=FALSE}
# 1. Extract rows 1 to 10
cereal[1:10, ]

# 2. Create new data frame with only Kelloggs cereals
Kelloggs <- cereal[cereal$company == "K", ]
Kelloggs

# 3. Names of cereals with more than 10 grams of sugar
cereal$name[cereal$sugars > 10]

# 4. Mean calories of all cereals
mean(cereal$calories)

# 5. Count cereals with fiber >= 2 grams
length(cereal$fiber[cereal$fiber >= 2])
# (alternative: sum(cereal$fiber >= 2))
```

<br><br><br>
